Category-based and location-based volitional covert attention affect memory at different timescales

### 2023-04-08 paper/main.tex
added a new response bias analysis comparing attended-category targets vs. lures in the sustained condition

Finally, we wondered whether participants' familiarity ratings might be
influenced in part by response bias effects. For example, a participant who had
recently received an ``attend to face images'' cue might rate even a novel face
image as more ``familiar'' if they leveraged their memory of the attention cue
(as opposed to solely relying on their memories of the composite images they
studied) to help guide their familiarity ratings. Indeed, participants in the
sustained attention condition do show some response biases. For example,
participants tended to rate novel images as more familiar if they came from the
just-cued category versus the unattended category (Fig.~\responseBias A; $t(29)
= 4.371, p < 0.001$). Responses biases are more difficult to evaluate in the
variable attention condition. For example, should cue recency be defined as the
number studied composite image pairs that came between the image whose
familiarity the participant is judging and the most recent same-category cue
(i.e., temporal distance to the nearest same-category attention cue)? Or might
response biases instead arise when a given category is cued more often near the
end of the just-studied list? We assigned each probed image a label based on
these two measures of category-matched cue recency. We then used linear
regressions of familiarity ratings on these recency measures to identify
potential response biases (Fig.~\responseBias B). Altogether we found no
evidence that participants in the variable attention condition tended to rate
images as more familiar solely due to how recently they had received a
same-category attention cue.

>>>>

Finally, we wondered whether participants' familiarity ratings might be
influenced in part by response bias effects. For example, a participant who had
recently received an ``attend to face images'' cue might rate even a novel face
image as more ``familiar'' if they leveraged their memory of the attention cue
(as opposed to solely relying on their memories of the composite images they
studied) to help guide their familiarity ratings. Indeed, participants in the
sustained attention condition do show some response biases. For example,
participants tended to rate novel images as more familiar if they came from the
just-cued category versus the unattended category (Fig.~\responseBias A; $t(29)
= 4.371, p < 0.001$). Nonetheless, participants' familiarity ratings in the
sustained attention condition cannot be explained solely by response biases.
For example, participants rate attended-category targets (i.e.,
attended-category images they encountered at the unattended location) as more
familiar than attended-category lures (i.e., attended-category novel images);
$t(29) = 2.645, p = 0.013$. Responses biases are more difficult to evaluate in
the variable attention condition. For example, should cue recency be defined as
the number studied composite image pairs that came between the image whose
familiarity the participant is judging and the most recent same-category cue
(i.e., temporal distance to the nearest same-category attention cue)? Or might
response biases instead arise when a given category is cued more often near the
end of the just-studied list? We assigned each probed image a label based on
these two measures of category-matched cue recency. We then used linear
regressions of familiarity ratings on these recency measures to identify
potential response biases (Fig.~\responseBias B). Altogether we found no
evidence that participants in the variable attention condition tended to rate
images as more familiar solely due to how recently they had received a
same-category attention cue.
